A New Unitary RG-based Auxiliary Model Approach to Strongly-Correlated Systems

### 2022-03-28 notes/notes.tex
introduced general filling and spin exchange between impurities

This difference in the type of conduction baths is utilised in dynamical mean-field theory to describe various phases of the bulk system. This is done through the DMFT algorithm: one starts with a non-interacting bath, but depending on the value of \(U\), the conduction bath then gets modified and we ultimately end up with something that is different from what we started with. For small\(U\), the bath does not change much and we retain the central resonance of the impurity spectral function. This then describes a metal in the bulk. For larger values of \(U\), however, the bath changes significantly such that its density of states becomes non-constant. Above a critical \(U_c\), the impurity spectral function gets gapped out, and that then describes the insulating phase in the bulk. \textit{This leaves open the following question: What is the minimal correlation one can insert into the non-interacting bath (of a single-impurity Anderson model) that can capture both the metallic and insulating phases of the bulk model?}

@@

\chapter{Physics of the generalised single-impurity Anderson model}
\label{chap:urg1}
\section{Introduction of spin-exchange and charge isospin-exchange interactions into the SIAM: the generalised SIAM}
We will now study the generalised SIAM obtained by introducing spin-exchange and charge isospin-exchange interactions between the impurity and the conduction bath. Such terms are generated when one does a Schrieffer-Wolff transformation on the SIAM, but we will find it prudent to keep these terms in the bare model itself.

@@

We can now define a temperature scale for the fixed-point theory:

@@

\section{Renormalization of impurity spectral function}
In this section we will obtain the impurity spectral function, which is defined in terms of the impurity Green's function as
\begin{equation}\begin{aligned}
	\mathcal{A(\omega)} = -\frac{1}{\pi}\text{ Im }\left[G_{dd}^\sigma\left( \omega \right) \right] 
\end{aligned}\end{equation}
The zero temperature retarded Green's function for the impurity, in the frequency domain, can be written as (see Appendix.~\ref{appx-spectral-func})
\begin{equation}\begin{aligned}
	\mathcal{A(\omega)} = \frac{1}{d_0}\sum_{n,0}\left[||\bra{0}\mathcal{O}_{\sigma}\ket{n}||^2\delta\left(\omega + E_0 - E_n\right) + ||\bra{n}\mathcal{O}_{\sigma}\ket{0}||^2\delta\left(\omega - E_0 + E_n\right)\right]
\end{aligned}\end{equation}
where \(\mathcal{O}_\sigma = c_{d\sigma} + S_d^- c_{0\overline\sigma} + S_d^z c_{0\sigma}\) is the excitation whose spectral function we are interested in. The excitations defined in \(\mathcal{O}\) incorporates both single-particle excitations brought about by the hybridisation as well as two-particle spin excitations brought about by the spin-exchange term
Since this is in terms of the exact eigenstates, it is a discrete sum of delta-functions. In practice, we get a continuous distribution. To compare with experiment, we need to convert the discrete sum into a continuous function. Following \cite{bullaNRGreview}, we replace the delta-functions at \(\pm x_n \equiv \pm(E_n - E_0)\) by normalized Gaussian functions
\begin{equation}\begin{aligned}
	\delta(\omega \pm x_n) \to \frac{1}{\eta_n\sqrt \pi}e^{-\left(\frac{\omega \pm x_n}{\eta_n}\right)^2}
\end{aligned}\end{equation}
The parameter \(\eta_n\) determines the height and width of the Gaussian, and is chosen such that the higher energy poles are broader than the lower energy ones:
\begin{equation}\begin{aligned}
	\eta_n = 4\Delta + \frac{1}{2}|x_n| 
\end{aligned}\end{equation}
\(\Delta = \pi \rho(0)V^2\) is the relevant energy scale for the non-interacting \((U=0)\) problem, \(\rho(0)\) being the density of states of the conduction bath at the Fermi energy. As a result, the function that we will numerically compute and plot is
\begin{equation}\begin{aligned}
	\mathcal{A(\omega)} &= \sum_{n,0}\frac{1}{d_0 \sqrt \pi \eta_n}\left[||\bra{0}c_{d\sigma}\ket{n}||^2e^{-\left(\frac{\omega - x_n}{\eta_n}\right)^2} + ||\bra{n}c_{d\sigma}\ket{0}||^2e^{-\left(\frac{\omega + x_n}{\eta_n}\right)^2}\right]
\end{aligned}\end{equation}
From the results of Langreth \cite{langreth1966}, we know that the spectral function at zero frequency is fixed by the occupancy of the impurity. Since we are in the particle-hole symmetric regime, this occupancy is fixed at 1, and hence so is the spectral function height at \(\omega = 0\). This result has been used to fix the spectral function height at the center during the computations. The fixed-point Hamiltonian \(H^*\) is diagonalized numerically to obtain \(\left\{E_n, \ket{n}\right\}\), for various values of the couplings. The intention here is to get an idea of how the spectral function morphs under the RG. Doing an actual reverse RG (described in \ref{rev_rg}) would require us to diagonalize a huge Hamiltonian. We take the simpler route of tuning the \(U\) from zero to soem large value. This should mimic the journey from the IR theory \((U=0)\) to the UV theory \((U \gg 0)\).

@@

\subsection*{Perturbation theory parameters}
\begin{center}
	\includegraphics[width=0.32\textwidth]{../figures/gap-t=1.000,J=1_over_U,V=3J,N=4,U=1.000,1.000,50.pdf}
	\includegraphics[width=0.32\textwidth]{../figures/par-t=1.000,J=1_over_U,V=3J,N=4,U=1.000,1.000,50.pdf}
	\includegraphics[width=0.32\textwidth]{../figures/lfl-t=1.000,J=1_over_U,V=3J,N=4,U=1.000,1.000,50.pdf}
\end{center}
The vanishing of the gap and the growth of the small parameter indicates the breakdown of perturbation theory around the singlet; this simply shows that there is a degeneracy in the local moment regime, and the effective Hamiltonian will have to be obtained using degenerate perturbation theory. The presence of degeneracy also suggests that the effective Hamiltonian will be of the non-Fermi liquid type.

@@

\subsection{Wilson ratio}
The Wilson ratio for the impurity is defined as
\begin{equation}\begin{aligned}
	R = \frac{\chi^s_{imp}}{\frac{C_{imp}}{T}}
\end{aligned}\end{equation}
From eq.~\eqref{rel_landau}, we have \(f_0^s = -f_0^a\), which, when combined with eq.~\eqref{fp_constraint}, gives
\begin{equation}\begin{aligned}
	\chi^s_{imp} &= 2\rho(0)_{imp}
\end{aligned}\end{equation}
The Wilson ratio becomes
\begin{equation}\begin{aligned}
	R = \frac{2\rho(0)_{imp}}{\rho(0)_{imp}} = 2
\end{aligned}\end{equation}

@@

Following Seki and Yunoki, we can define a winding number for a Green's function \(G(z)\):

@@

The first process is the forward RG which we used to obtain the scaling equations. The second process is the reverse RG which we will undertake now. In general, we start with an IR wavefunction that consists a certain number of momentum states \(n_1\) still entangled with the impurity, and the remaining momentum states \(n_2\) disentangled from the impurity. The former are said to be part of the emergent Kondo cloud, while the latter are said to be part of the integrals of motion (IOMs) and appear in direct product with the cloud+impurity system in the ground state wavefunction. Each momentum state is tagged with two conduction bath levels, one above the Fermi surface and one below. These will be represented as \(k,\pm\). If we represent the emergent cloud momentum states as \(\left\{k_i\right\} \) and the IOM states as \(\left\{q_i\right\}\), the ground state wavefunction can be written as 

@@

\subsection*{Perturbation theoretic terms}
These quantities are related to the local Fermi liquid of the Kondo strong coupling fixed point and the perturbation theory associated with it. \(min(\delta E)\) is the gap in the spectrum of the two-site Hamiltonian; this which acts as the denominator for the perturbation theoretic calculations. \(t^2/\delta E\) is the small parameter for the expansion, \(t\) being the tight-binding hopping. \(\mathcal{F}\) is the strength of the local Fermi liquid \((\mathcal{F} \hat n_{1 \uparrow} \hat n_{1 \downarrow})\).
\begin{center}
	\includegraphics[width=0.32\textwidth]{../figures/gap-t=1.000,J=10.000,0.000,40,V=3J,Ubath=-U_by_10,N=4,U=1.000,1000.000,40.pdf}
	\includegraphics[width=0.32\textwidth]{../figures/par-t=1.000,J=10.000,0.000,40,V=3J,Ubath=-U_by_10,N=4,U=1.000,1000.000,40.pdf}
	\includegraphics[width=0.32\textwidth]{../figures/lfl-t=1.000,J=10.000,0.000,40,V=3J,Ubath=-U_by_10,N=4,U=1.000,1000.000,40.pdf}
\end{center}

\subsection*{Correlation within the Kondo cloud}
\begin{center}
	\includegraphics[width=0.32\textwidth]{../figures/corr-k-t=1.000,J=10.000,0.000,40,V=3J,Ubath=-U_by_10,N=4,U=1.000,1000.000,40.pdf}
	\includegraphics[width=0.32\textwidth]{../figures/mi-dk-t=1.000,J=10.000,0.000,40,V=3J,Ubath=-U_by_10,N=4,U=1.000,1000.000,40.pdf}
	\includegraphics[width=0.32\textwidth]{../figures/corr-k-diag-t=1.000,J=10.000,0.000,40,V=3J,Ubath=-U_by_10,N=4,U=1.000,1000.000,40.pdf}
	\includegraphics[width=0.32\textwidth]{../figures/corr-k-od-t=1.000,J=10.000,0.000,40,V=3J,Ubath=-U_by_10,N=4,U=1.000,1000.000,40.pdf}
\end{center}

\subsection*{Mutual information between various real space members}
\begin{center}
	\includegraphics[width=0.32\textwidth]{../figures/mi-01-t=1.000,J=10.000,0.000,40,V=3J,Ubath=-U_by_10,N=4,U=1.000,1000.000,40.pdf}
	\includegraphics[width=0.32\textwidth]{../figures/mi-d0-t=1.000,J=10.000,0.000,40,V=3J,Ubath=-U_by_10,N=4,U=1.000,1000.000,40.pdf}
	\includegraphics[width=0.32\textwidth]{../figures/mi-d1-t=1.000,J=10.000,0.000,40,V=3J,Ubath=-U_by_10,N=4,U=1.000,1000.000,40.pdf}
\end{center}

@@

\begin{center}
	\includegraphics[width=0.32\textwidth]{../figures/EE-d-t=1.000,J=10.000,0.000,40,V=3J,Ubath=-U_by_10,N=4,U=1.000,1000.000,40.pdf}
	\includegraphics[width=0.32\textwidth]{../figures/corr-d0-t=1.000,J=10.000,0.000,40,V=3J,Ubath=-U_by_10,N=4,U=1.000,1000.000,40.pdf}
	\includegraphics[width=0.32\textwidth]{../figures/corr-d1-t=1.000,J=10.000,0.000,40,V=3J,Ubath=-U_by_10,N=4,U=1.000,1000.000,40.pdf}
	\includegraphics[width=0.32\textwidth]{../figures/r-vec-corr-01-t=1.000,J=10.000,0.000,40,V=3J,Ubath=-U_by_10,N=4,U=1.000,1000.000,40.pdf}
	\includegraphics[width=0.32\textwidth]{../figures/r-vec-corr-02-t=1.000,J=10.000,0.000,40,V=3J,Ubath=-U_by_10,N=4,U=1.000,1000.000,40.pdf}
	\includegraphics[width=0.32\textwidth]{../figures/r-vec-corr-03-t=1.000,J=10.000,0.000,40,V=3J,Ubath=-U_by_10,N=4,U=1.000,1000.000,40.pdf}

@@

\subsection*{Real-space correlations}
\begin{center}
	\includegraphics[width=0.32\textwidth]{../figures/r1p-t=1.000,J=10.000,0.000,40,V=3J,Ubath=-U_by_10,N=4,U=1.000,1000.000,40.pdf}
	\includegraphics[width=0.32\textwidth]{../figures/r-od-t=1.000,J=10.000,0.000,40,V=3J,Ubath=-U_by_10,N=4,U=1.000,1000.000,40.pdf}
	\includegraphics[width=0.32\textwidth]{../figures/r-opp-t=1.000,J=10.000,0.000,40,V=3J,Ubath=-U_by_10,N=4,U=1.000,1000.000,40.pdf}

	\includegraphics[width=0.3\textwidth]{../figures/r-par-t=1.000,J=10.000,0.000,40,V=3J,Ubath=-U_by_10,N=4,U=1.000,1000.000,40.pdf}
	\includegraphics[width=0.3\textwidth]{../figures/r-ising-t=1.000,J=10.000,0.000,40,V=3J,Ubath=-U_by_10,N=4,U=1.000,1000.000,40.pdf}
	\includegraphics[width=0.3\textwidth]{../figures/r-charge-t=1.000,J=10.000,0.000,40,V=3J,Ubath=-U_by_10,N=4,U=1.000,1000.000,40.pdf}
\end{center}

@@

Previously, we have worked out the grounstate phases of a single-impurity model with an interacting bath:
	\label{siam_attr}
	\mathcal{H}_\text{aux} = \sum_{k\sigma}\epsilon_k \tau_{k\sigma} - \frac{U}{2}\left( \hat n_{d \uparrow} - \hat n_{d \downarrow} \right) ^2 + \sum_{k\sigma} \left(V_{k} c^\dagger_{k\sigma} c_{d\sigma} + h.c.\right) +J \vec{S_d}\cdot\vec{s} - U_b\left(\hat n_{0 \uparrow} - \hat n_{0 \downarrow}\right)^2 
We will use this as the auxiliary model to study the Hubbard model. We do this by first recreating the Hubbard model upon tiling the lattice with instances of this auxiliary model Hamiltonian. To begin this procedure, we first create the unit of tiling - this is done by identifying the impurity as a particular site \(i\) of the lattice, and the bath coupled to the impurity as the set of remaining \(N-1\) sites in the lattice. We will also identity the zeroth site of the SIAM lattice as one of the nearest neighbours \(j\) of \(i\):

@@

	\mathcal{H}_{H-H} = -\sum_{i} U_H \left(\hat n_{i \uparrow} - \hat n_{i \downarrow} \right)^2 - t_H\sum_{<i,j>,\sigma}\left(c^\dagger_{i\sigma}c_{j\sigma} + \text{h.c.}\right) + J_H\sum_{<i,j>} \vec{S}_i\cdot\vec{S}_j

@@

@@

\begin{figure}[!htb]
\centering
	\includegraphics[width=0.3\textwidth]{../figures/corr-k-t=1.000,J=31.623,0.000,50,V=2J,Ubath=-U,N=4,U=0.032,3.162,50.pdf}
	\includegraphics[width=0.3\textwidth]{../figures/corr-d0-t=1.000,J=31.623,0.000,50,V=2J,Ubath=-U,N=4,U=0.032,3.162,50.pdf}
	\includegraphics[width=0.3\textwidth]{../figures/r1p-t=1.000,J=31.623,0.000,50,V=2J,Ubath=-U,N=4,U=0.032,3.162,50.pdf}
	\caption{Evolution of correlation functions and mutual information across the transition.}
\end{figure}

@@

\section{Creating \(N-\)site Hubbard Hamiltonian from Hubbard dimer embedded in a bath}
Similar to the previous chapterm, we will now tile the lattice with the two-site auxiliary model
\begin{equation}\begin{aligned}
	H_\text{aux} = \sum_{i=1,2} \left[- \frac{U}{2}\left(\hat n_{d_i \uparrow} - \hat n_{d_i \downarrow}\right)^2 + V\sum_{\sigma}\left(c^\dagger_{d_i\sigma}c_{0_i\sigma} + \text{h.c.}\right) + J \vec{S}_{d_i}\cdot\vec{s}_{0_i} - U_b\left(\hat n_{0_i \uparrow} - \hat n_{0_i \downarrow}\right)^2\right]\\
	 -t \sum_\sigma \left(c^\dagger_{d_1,\sigma}c_{d_2,\sigma} + \text{h.c.}\right) + \sum_{k\sigma}\epsilon_k \tau_{k\sigma}
\end{aligned}\end{equation}
For concreteness, we will consider a lattice of \(N\) lattice sites and \(w\) nearest neighbours for each site. Note that a uniform number of nearest neighbours means that there is perfect translational invariance on the lattice, which means there cannot be any edge sites. This is achieved by applying periodic boundary conditions on the edges of the lattice. For example, a square 2d lattice will have to be placed on a 2-torus.

@@

>>>>

This difference in the type of conduction baths is utilised in dynamical mean-field theory to describe various phases of the bulk system.
This is done through the DMFT algorithm: one starts with a non-interacting bath, but depending on the value of \(U\), the conduction bath then gets modified and we ultimately end up with something that is different from what we started with.
For small \(U\), the bath does not change much and we retain the central resonance of the impurity spectral function.
This then describes a metal in the bulk.
For larger values of \(U\), however, the bath changes significantly such that its density of states becomes non-constant.
Above a critical \(U_c\), the impurity spectral function gets gapped out, and that then describes the insulating phase in the bulk.
\textit{This leaves open the following question: What is the minimal correlation one can insert into the non-interacting bath (of a single-impurity Anderson model) that can capture both the metallic and insulating phases of the bulk model?}

@@

\chapter{Physics of the generalised single-impurity Anderson model}
\label{chap:urg1}
\section{Introduction of spin-exchange and charge isospin-exchange interactions into the SIAM: the generalised SIAM}
We will now study the generalised SIAM obtained by introducing spin-exchange and charge isospin-exchange interactions between the impurity and the conduction bath~\cite{zitko_2006}. Such terms are generated when one does a Schrieffer-Wolff transformation on the SIAM, but we will find it prudent to keep these terms in the bare model itself.

@@

We can now define a temperature scale~\cite{wilson1975,hrk_wilson_1980} for the fixed-point theory:

@@

\section{Renormalization of impurity spectral function}
In this section we will obtain the impurity spectral function~\cite{costi2000,rosch_costi2003,bullaNRGreview}, which is defined in terms of the impurity Green's function as
\begin{equation}\begin{aligned}
	\mathcal{A(\omega)} = -\frac{1}{\pi}\text{ Im }\left[G_{dd}^\sigma\left( \omega \right) \right] 
\end{aligned}\end{equation}
The zero temperature retarded Green's function for the impurity, in the frequency domain, can be written as (see Appendix.~\ref{appx-spectral-func})
\begin{equation}\begin{aligned}
	\mathcal{A(\omega)} = \frac{1}{d_0}\sum_{n,0}\left[||\bra{0}\mathcal{O}_{\sigma}\ket{n}||^2\delta\left(\omega + E_0 - E_n\right) + ||\bra{n}\mathcal{O}_{\sigma}\ket{0}||^2\delta\left(\omega - E_0 + E_n\right)\right]
\end{aligned}\end{equation}
where \(\mathcal{O}_\sigma = c_{d\sigma} + S_d^- c_{0\overline\sigma} + S_d^z c_{0\sigma}\) is the excitation whose spectral function we are interested in. The excitations defined in \(\mathcal{O}\) incorporates both single-particle excitations brought about by the hybridisation as well as two-particle spin excitations brought about by the spin-exchange term
Since this is in terms of the exact eigenstates, it is a discrete sum of delta-functions. In practice, we get a continuous distribution. To compare with experiment, we need to convert the discrete sum into a continuous function. Following \cite{bullaNRGreview}, we replace the delta-functions at \(\pm x_n \equiv \pm(E_n - E_0)\) by normalized Gaussian functions
\begin{equation}\begin{aligned}
	\delta(\omega \pm x_n) \to \frac{1}{\eta_n\sqrt \pi}e^{-\left(\frac{\omega \pm x_n}{\eta_n}\right)^2}
\end{aligned}\end{equation}
The parameter \(\eta_n\) determines the height and width of the Gaussian, and is chosen such that the higher energy poles are broader than the lower energy ones:
\begin{equation}\begin{aligned}
	\eta_n = 4\Delta + \frac{1}{2}|x_n| 
\end{aligned}\end{equation}
\(\Delta = \pi \rho(0)V^2\) is the relevant energy scale for the non-interacting \((U=0)\) problem, \(\rho(0)\) being the density of states of the conduction bath at the Fermi energy. As a result, the function that we will numerically compute and plot is
\begin{equation}\begin{aligned}
	\mathcal{A(\omega)} &= \sum_{n,0}\frac{1}{d_0 \sqrt \pi \eta_n}\left[||\bra{0}c_{d\sigma}\ket{n}||^2e^{-\left(\frac{\omega - x_n}{\eta_n}\right)^2} + ||\bra{n}c_{d\sigma}\ket{0}||^2e^{-\left(\frac{\omega + x_n}{\eta_n}\right)^2}\right]
\end{aligned}\end{equation}
From the results of Langreth \cite{langreth1966}, we know that the spectral function at zero frequency is fixed by the occupancy of the impurity. Since we are in the particle-hole symmetric regime, this occupancy is fixed at 1, and hence so is the spectral function height at \(\omega = 0\). This result has been used to fix the spectral function height at the center during the computations. The fixed-point Hamiltonian \(H^*\) is diagonalized numerically to obtain \(\left\{E_n, \ket{n}\right\}\), for various values of the couplings. The intention here is to get an idea of how the spectral function morphs under the RG. Doing an actual reverse RG (described in \ref{rev_rg}) would require us to diagonalize a huge Hamiltonian. We take the simpler route of tuning the \(U\) from zero to soem large value. This should mimic the journey from the IR theory \((U=0)\) to the UV theory \((U \gg 0)\).

@@

\subsection*{Perturbation theory parameters}
\begin{center}
	\includegraphics[width=0.32\textwidth]{../figures/gap-t=1.000,U=1,V=3J,N=6,J=100.000,0.010,40.pdf}
	\includegraphics[width=0.32\textwidth]{../figures/par-t=1.000,U=1,V=3J,N=6,J=100.000,0.010,40.pdf}
	\includegraphics[width=0.32\textwidth]{../figures/lfl-t=1.000,U=1,V=3J,N=6,J=100.000,0.010,40.pdf}
\end{center}
The vanishing of the gap and the growth of the small parameter indicates the breakdown of perturbation theory around the singlet; this simply shows that there is a degeneracy in the local moment regime, and the effective Hamiltonian will have to be obtained using degenerate perturbation theory. The presence of degeneracy also suggests that the effective Hamiltonian will be of the non-Fermi liquid type.

@@

\subsection{Wilson ratio}
The Wilson ratio for the impurity~\cite{wilson1975,nozieres1974fermi,hewson1993} is defined as
\begin{equation}\begin{aligned}
	R = \frac{\chi^s_{imp}}{\frac{C_{imp}}{T}}
\end{aligned}\end{equation}
From eq.~\eqref{rel_landau}, we have \(f_0^s = -f_0^a\), which, when combined with eq.~\eqref{fp_constraint}, gives
\begin{equation}\begin{aligned}
	\chi^s_{imp} &= 2\rho(0)_{imp}
\end{aligned}\end{equation}
The Wilson ratio becomes
\begin{equation}\begin{aligned}
	R = \frac{2\rho(0)_{imp}}{\rho(0)_{imp}} = 2
\end{aligned}\end{equation}

@@

Following Seki and Yunoki~\cite{seki2017topological}, we can define a winding number for a Green's function \(G(z)\):

@@

The first process is the forward RG which we used to obtain the scaling equations.
The second process is the reverse RG which we will undertake now. The method has already been applied to study the renormalisation of entanglement in various models of strong correlation~\cite{siddharthacpi,anirban_kondo,anirban_mott_ent}.
In general, we start with an IR wavefunction that consists a certain number of momentum states \(n_1\) still entangled with the impurity, and the remaining momentum states \(n_2\) disentangled from the impurity.
The former are said to be part of the emergent Kondo cloud, while the latter are said to be part of the integrals of motion (IOMs) and appear in direct product with the cloud+impurity system in the ground state wavefunction.
Each momentum state is tagged with two conduction bath levels, one above the Fermi surface and one below.
These will be represented as \(k,\pm\). If we represent the emergent cloud momentum states as \(\left\{k_i\right\} \) and the IOM states as \(\left\{q_i\right\}\), the ground state wavefunction can be written as 

@@

\subsection*{Perturbation theoretic terms}
These quantities are related to the local Fermi liquid of the Kondo strong coupling fixed point and the perturbation theory associated with it. \(min(\delta E)\) is the gap in the spectrum of the two-site Hamiltonian; this which acts as the denominator for the perturbation theoretic calculations. \(t^2/\delta E\) is the small parameter for the expansion, \(t\) being the tight-binding hopping. \(\mathcal{F}\) is the strength of the local Fermi liquid \((\mathcal{F} \hat n_{1 \uparrow} \hat n_{1 \downarrow})\).
\begin{center}
	\includegraphics[width=0.32\textwidth]{../figures/gap-t=1.000,J=10.000,0.000,30,V=3J,Ubath=-U_by_10,N=6,U=1.000,889.513,30.pdf}
	\includegraphics[width=0.32\textwidth]{../figures/par-t=1.000,J=10.000,0.000,30,V=3J,Ubath=-U_by_10,N=6,U=1.000,889.513,30.pdf}
	\includegraphics[width=0.32\textwidth]{../figures/lfl-t=1.000,J=10.000,0.000,30,V=3J,Ubath=-U_by_10,N=6,U=1.000,889.513,30.pdf}
\end{center}

\subsection*{Correlation within the Kondo cloud}
\begin{center}
	\includegraphics[width=0.32\textwidth]{../figures/corr-k-t=1.000,J=10.000,0.000,30,V=3J,Ubath=-U_by_10,N=6,U=1.000,889.513,30.pdf}
	\includegraphics[width=0.32\textwidth]{../figures/mi-dk-t=1.000,J=10.000,0.000,30,V=3J,Ubath=-U_by_10,N=6,U=1.000,889.513,30.pdf}
	\includegraphics[width=0.32\textwidth]{../figures/corr-k-diag-t=1.000,J=10.000,0.000,30,V=3J,Ubath=-U_by_10,N=6,U=1.000,889.513,30.pdf}
	\includegraphics[width=0.32\textwidth]{../figures/corr-k-od-t=1.000,J=10.000,0.000,30,V=3J,Ubath=-U_by_10,N=6,U=1.000,889.513,30.pdf}
\end{center}

\subsection*{Mutual information between various real space members}
\begin{center}
	\includegraphics[width=0.32\textwidth]{../figures/mi-01-t=1.000,J=10.000,0.000,30,V=3J,Ubath=-U_by_10,N=6,U=1.000,889.513,30.pdf}
	\includegraphics[width=0.32\textwidth]{../figures/mi-d0-t=1.000,J=10.000,0.000,30,V=3J,Ubath=-U_by_10,N=6,U=1.000,889.513,30.pdf}
	\includegraphics[width=0.32\textwidth]{../figures/mi-d1-t=1.000,J=10.000,0.000,30,V=3J,Ubath=-U_by_10,N=6,U=1.000,889.513,30.pdf}
\end{center}

@@

\begin{center}
	\includegraphics[width=0.32\textwidth]{../figures/EE-d-t=1.000,J=10.000,0.000,30,V=3J,Ubath=-U_by_10,N=6,U=1.000,889.513,30.pdf}
	\includegraphics[width=0.32\textwidth]{../figures/corr-d0-t=1.000,J=10.000,0.000,30,V=3J,Ubath=-U_by_10,N=6,U=1.000,889.513,30.pdf}
	\includegraphics[width=0.32\textwidth]{../figures/corr-d1-t=1.000,J=10.000,0.000,30,V=3J,Ubath=-U_by_10,N=6,U=1.000,889.513,30.pdf}
	\includegraphics[width=0.32\textwidth]{../figures/r-vec-corr-01-t=1.000,J=10.000,0.000,30,V=3J,Ubath=-U_by_10,N=6,U=1.000,889.513,30.pdf}
	\includegraphics[width=0.32\textwidth]{../figures/r-vec-corr-02-t=1.000,J=10.000,0.000,30,V=3J,Ubath=-U_by_10,N=6,U=1.000,889.513,30.pdf}
	\includegraphics[width=0.32\textwidth]{../figures/r-vec-corr-03-t=1.000,J=10.000,0.000,30,V=3J,Ubath=-U_by_10,N=6,U=1.000,889.513,30.pdf}

@@

\subsection*{Real-space correlations}
\begin{center}
	\includegraphics[width=0.32\textwidth]{../figures/r1p-t=1.000,J=10.000,0.000,30,V=3J,Ubath=-U_by_10,N=6,U=1.000,889.513,30.pdf}
	\includegraphics[width=0.32\textwidth]{../figures/r-od-t=1.000,J=10.000,0.000,30,V=3J,Ubath=-U_by_10,N=6,U=1.000,889.513,30.pdf}
	\includegraphics[width=0.32\textwidth]{../figures/r-opp-t=1.000,J=10.000,0.000,30,V=3J,Ubath=-U_by_10,N=6,U=1.000,889.513,30.pdf}

	\includegraphics[width=0.3\textwidth]{../figures/r-par-t=1.000,J=10.000,0.000,30,V=3J,Ubath=-U_by_10,N=6,U=1.000,889.513,30.pdf}
	\includegraphics[width=0.3\textwidth]{../figures/r-ising-t=1.000,J=10.000,0.000,30,V=3J,Ubath=-U_by_10,N=6,U=1.000,889.513,30.pdf}
	\includegraphics[width=0.3\textwidth]{../figures/r-charge-t=1.000,J=10.000,0.000,30,V=3J,Ubath=-U_by_10,N=6,U=1.000,889.513,30.pdf}
\end{center}

@@

Previously, we have worked out the grounstate phases of a single-impurity model with an interacting bath:
\begin{equation}\begin{aligned}
	\label{siam_attr}
	\mathcal{H}_\text{aux} = \sum_{k\sigma}\epsilon_k \tau_{k\sigma} - \frac{U}{2}\left(\hat n_{d \uparrow} - \hat n_{d \downarrow} \right) ^2 + \sum_{k\sigma} \left(V_{k} c^\dagger_{k\sigma} c_{d\sigma} + h.c.\right) +J \vec{S_d}\cdot\vec{s} - U_b\left(\hat n_{0 \uparrow} - \hat n_{0 \downarrow}\right)^2 
\end{aligned}\end{equation}

We will use this as the auxiliary model to study the Hubbard model. We do this by first recreating the Hubbard model upon tiling the lattice with instances of this auxiliary model Hamiltonian. Note that the impurity level is explicitly at half-filling, because the correlation term \(\left( \hat n_{d \uparrow} - \hat n_{d \downarrow} \right) ^2\) is symmetric under a particle-hole transformation \(\hat n_{d\sigma} \to 1 - \hat n_{d\sigma}\). Moreover, the conduction bath is also at half-filling, because we have set the chemical potential \(\mu\) to zero. These two ensure that the bulk model is also at half-filling. At the end of this section, we will also mention how the tiling works out in the presence of a non-zero filling.

To begin this procedure, we first create the unit of tiling - this is done by identifying the impurity as a particular site \(i\) of the lattice, and the bath coupled to the impurity as the set of remaining \(N-1\) sites in the lattice. We will also identity the zeroth site of the SIAM lattice as one of the nearest neighbours \(j\) of \(i\):

@@

	\mathcal{H}_{H-H} = -\sum_{i} U_\text{H-H} \left(\hat n_{i \uparrow} - \hat n_{i \downarrow} \right)^2 - t_\text{H-H}\sum_{<i,j>,\sigma}\left(c^\dagger_{i\sigma}c_{j\sigma} + \text{h.c.}\right) + J_\text{H-H}\sum_{<i,j>} \vec{S}_i\cdot\vec{S}_j

@@

As mentioned before, no chemical potential \(\mu\) is generated becuase the auxiliary model was at half-filling, both in the impurity as well as in the bath. We can change the chemical potential by introducing two terms:
\begin{equation}\begin{aligned}
	\eta \sum_\sigma\left(n_{d\sigma} - \frac{1}{2}\right), \mu \sum_{i,\sigma}\left(\hat n_{i\sigma} - \frac{1}{2}\right)
\end{aligned}\end{equation}
The first term is the particle-hole asymmetry term, and tuning that term moves the impurity away from half-filling. The second term is the usual chemical potential in the bath. Introducing these terms in the auxiliary model changes the bulk model into:
\begin{equation}\begin{aligned}
	\mathcal{H}_{H-H} = -\sum_{i} U_\text{H-H} \left(\hat n_{i \uparrow} - \hat n_{i \downarrow} \right)^2 - t_\text{H-H}\sum_{<i,j>,\sigma}\left(c^\dagger_{i\sigma}c_{j\sigma} + \text{h.c.}\right) + J_\text{H-H}\sum_{<i,j>} \vec{S}_i\cdot\vec{S}_j + \mu_\text{H-H}\sum_{i\sigma}\left(\hat n_{i\sigma} - \frac{1}{2}\right) 
\end{aligned}\end{equation}
The only change is the generation of the last term. The mappings between the existing parameters and their auxiliary model counterparts remain the same, while \(\mu_\text{H-H}\) is given by
\begin{equation}\begin{aligned}
	\mu_\text{H-H} = \eta + \left(N-1\right) \mu
\end{aligned}\end{equation}
In the discussion henceforth, we will assume all the models are at half-filling. We will come back to the doped case at a later point in time.

@@

\begin{figure}[!htb]
\centering
	\includegraphics[width=0.3\textwidth]{../figures/corr-k-t=1.000,J=10.000,0.000,30,V=3J,Ubath=-U_by_10,N=6,U=1.000,889.513,30.pdf}
	\includegraphics[width=0.3\textwidth]{../figures/corr-d0-t=1.000,J=10.000,0.000,30,V=3J,Ubath=-U_by_10,N=6,U=1.000,889.513,30.pdf}
	\includegraphics[width=0.3\textwidth]{../figures/r1p-t=1.000,J=10.000,0.000,30,V=3J,Ubath=-U_by_10,N=6,U=1.000,889.513,30.pdf}
	\caption{Evolution of correlation functions and mutual information across the transition.}
\end{figure}

@@

\section{Creating \(N-\)site Hubbard Hamiltonian from Hubbard dimer embedded in a bath}
Similar to the previous chapter, we will now tile the lattice with the two-site auxiliary model
\begin{equation}\begin{aligned}
	H_\text{aux} = \sum_{i=1,2} \left[- \frac{U}{2}\left(\hat n_{d_i \uparrow} - \hat n_{d_i \downarrow}\right)^2 + V\sum_{\sigma}\left(c^\dagger_{d_i\sigma}c_{0_i\sigma} + \text{h.c.}\right) + J \vec{S}_{d_i}\cdot\vec{s}_{0_i} - U_b\left(\hat n_{0_i \uparrow} - \hat n_{0_i \downarrow}\right)^2\right]\\
	 -t \sum_\sigma \left(c^\dagger_{d_1,\sigma}c_{d_2,\sigma} + \text{h.c.}\right) + \sum_{k\sigma}\epsilon_k \tau_{k\sigma}
\end{aligned}\end{equation}
For concreteness, we will consider a lattice of \(N\) lattice sites and \(w\) nearest neighbours for each site. Note that a uniform number of nearest neighbours means that there is perfect translational invariance on the lattice, which means there cannot be any edge sites. This is achieved by applying periodic boundary conditions on the edges of the lattice. For example, a square 2d lattice will have to be placed on a 2-torus.

@@

We could have also inserted a spin-exchange interaction between the two impurities in the auxiliary model:
\begin{equation}\begin{aligned}
	H_\text{aux} = \sum_{i=1,2} \left[- \frac{U}{2}\left(\hat n_{d_i \uparrow} - \hat n_{d_i \downarrow}\right)^2 + V\sum_{\sigma}\left(c^\dagger_{d_i\sigma}c_{0_i\sigma} + \text{h.c.}\right) + J \vec{S}_{d_i}\cdot\vec{s}_{0_i} - U_b\left(\hat n_{0_i \uparrow} - \hat n_{0_i \downarrow}\right)^2\right] -t \sum_\sigma \left(c^\dagger_{d_1,\sigma}c_{d_2,\sigma} + \text{h.c.}\right)\\
	+ J_d \vec{S}_{d_1}\cdot\vec{S}_{d_2} + \sum_{k\sigma}\epsilon_k \tau_{k\sigma}
\end{aligned}\end{equation}
In the presence of this term, the bulk Hamiltonian remains the same, but the expression of \(J_\text{H-H}\) changes. Since this term is similar in form to the term preceding it, we can easily obtain the updated expression:
\begin{equation}\begin{aligned}
	J_\text{H-H} = \frac{2}{w}\left(4J + 2J_d\right)
\end{aligned}\end{equation}
